Article Summaries

### 2025-02-04 articleSummaries.qmd
Updated articles

>>>>

[@wang2025] The goal of the paper is to try and find a connection between the salt intake of an individual and if they will develop anxiety or depression later in life. Depression and anxiety are extremely prevalent in our society today and we are prone to eating salt with every meal, especially in the United States. Determining an association between salt and mental health will allow professionals an area to ask their patients to assist them with their mental health. In addition, salt is known to be harmful in large quantities to our health overall so this would be another area to encourage a decrease in salt intake. The group took almost half a million participants who, at the start of the study, had never been diagnosed with depression or anxiety and had no missing data. The participants were asked if they added salt to their foods and to note how often they do and major changes to their diet, if any. They first found the mean with SD and used the chi-square tests for categorical variables and general linear models for continuous variables to check the proportions between their participants and their salt intake level. They then used the Cox proportional hazards for the association between an individual's salt intake and the risk of developing depression or anxiety. They tested the assumption using the Kaplan-Meier method and Schoenfeld residuals and found no violation. They looked at the analyses with hazard ratios and did multiplicative interaction assessments in the Cox models. They also conducted several sensitivity tests to make adjustments. The results showed that hazard of depression did increase with the increased intake of salt. A similar result was found for anxiety and increased salt. The limitations of this particular study included the self-reporting of a person's salt intake, their sociodemographic factors, and their lifestyle factors. Primarily, the limitations for this paper were based on possible bias in their data.

[@zhang2025] The goal of the paper is to determine an association with postpartum depression and having two or more chronic diseases (called multimorbidity). This is important because many women suffer from postpartum depression and this can have lasting affects on their lives. In addition, understanding the long term implications of postpartum depression could help in preparing women for what might happen with childbirth and the mental impact it can have. The data was provided by self reporting. Women noted if they had a depressive episode in the months after giving birth or if they were told they had postpartum depression. They selected 36 chronic diseases to focus on and used the prevalence of multimorbidity, the incidence of multimorbidity, the number of new-onset chronic diseases, the cumulative rate of chronic diseases, and the multimorbidity patterns as the specific outcomes they were measuring. They provided the list of covariates within the paper. They first used binomial logistic regression models and quasi-Poisson mixed effects models to assist in gaining the initial findings of the study and create a baseline. They used Cox proportional hazard models to evaluate the associations of postpartum depression with having developed one or more of their chronic diseases. They checked the proportional hazard assumption using Schoenfeld's residual methods and no violations were found. They then used multinomial logistic regression models to study the association between postpartum depression and the five multimorbidity patterns they were able to determine. Patients who had a history of postpartum depression were shown to have a higher rate prevalence and incidence of one or more of the chronic diseases. They also discovered that those who had multimorbidity as their baseline prior to the study had a higher rate of prevalence and incidence as well. The limitations of this study are similar to those in the salt and anxiety study as their data came from the same place in both studies. As such, the data was open to bias and issues with self-reporting from the patients. The data also limited the representation of women due to various factors.

-   What is the goal of the paper?

-   Why is it important?

-   How is it solved? - methods

-   Results/limitations, if any.
